Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-18 paper/paper.tex
pass on eval

This section evaluates the precision and efficiency of \tname{}.

@@

\vspace{1ex}
\noindent
\textbf{Malicious traffic.}~Nikto?\Fix{where do these
  attacks/messages come from?}
  \Luc{Nós executamos um servidor http (Apache2) numa maquina e executamos o Nikto em outra maquina atacando o servidor http. Capturamos o trafego q chegava ao servidor e eh ele q estamos utilizando.}

\vspace{1ex}
\noindent
\textbf{Benign traffic.}~\tname{} uses public databases storing benign
traffic for all protocols covered by Suricata (see
Figure~\ref{fig:distribution-rules-protocol}). We used two datasets of
positive traffic. The Bigflows.pcap dataset is part of the
TcpReplay~\cite{tcpreplay} open source project. This dataset includes
real network traffic on a busy private network access point to the
Internet. According to the TcpReplay web site ``This capture is much
larger and has a smaller average packet size than the previous capture
(smallFlows.pcap). It also has many more flows and different
applications.''. In addition to the Bigflows.pcap dataset, we also
used datasets of normal traffic made available by Stratosphere
Lab~\cite{stratosphere-normal}.

\vspace{1ex}
\noindent
\textbf{Ground Truth.}~The rules that detect those attacks were
obtained from the Emerging Threats Open
Ruleset~\cite{emerging-threats-open}.

@@

\begin{table*}[h]
  \caption{\label{table:attacks}List of attacks.\Mar{Guilherme, por
      favor, adicione mais ataques aqui...}}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth} \\
    \midrule     
    Ping Scan \MyComment{& single} & ICMP \MyComment{& Discovers
      active hosts in a network} & \scriptsize{dsize:0; itype:8;} \\
    Black Nurse \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:3; icode:3; detection\_filter:track by\_dst, count 250, seconds 1;}\\
    Ping Flood  \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:8; icode:0; detection\_filter:track by\_src, count 30, seconds 1;}\\  
    Port Scan \MyComment{& single} & TCP \MyComment{& Discovers open ports in a host} & \scriptsize{flags: A; ack: 0;dsize: 0;} \\
    SYN Flood \MyComment{& multiple} & TCP \MyComment{& Denial of Service} & \scriptsize{flags: S,12; threshold: type both, track by\_dst, count 5000, seconds 5;}\\
    UDP Flood \MyComment{& multiple} & UDP \MyComment{& Denial of Service} & \scriptsize{fragbits:M; threshold: type both, track by\_dst, count 5000, seconds 5;} \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

\subsubsection{Attack reproduction.} \tname{} requires the attack to
be replayed in order to check whether or not the rule it generates
captures the attack.  See function $\mathit{isPlausible}$, used in the
minimization algorithm from Section~\ref{sec:minimization}. For all
attacks listed on Table~\ref{table:attacks}, we found scripts
available on the web to replay the attacks. For example, the SYN Flood
attack can be replayed with hping3~\cite{hping3}, using the following
command: \CodeIn{hping3 -d 80 -w 64 -S -p 80 --flood --rand-source
  <IP>}. With the script to reproduce the attack, we executed the
following steps to obtain ``pcap'' files, which abstracts network
messages~\cite{pcap}, to run \tname:~1)~instantiate the script (\eg{},
define the IP, for the example above), 2)~execute the script,
3)~monitor the traffic with the wireshark network
monitor~\cite{wireshark-net-monitor}.

@@

\subsection{Precision}

\Fix{}

\subsection{Efficiency}

>>>>

\begin{table*}[h!]
  \caption{\label{table:attacks}List of attacks.\Mar{Guilherme, por
      favor, adicione mais ataques aqui...}}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{1}{c}{Name} &
    \multicolumn{1}{c}{Protocol} &
    \multicolumn{1}{c}{Groud Truth} \\
    \midrule     
    Ping Scan \MyComment{& single} & ICMP \MyComment{& Discovers
      active hosts in a network} & \scriptsize{dsize:0; itype:8;} \\
    Black Nurse \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:3; icode:3; detection\_filter:track by\_dst, count 250, seconds 1;}\\
    Ping Flood  \MyComment{& multiple} & ICMP \MyComment{& Denial of Service} & \scriptsize{itype:8; icode:0; detection\_filter:track by\_src, count 30, seconds 1;}\\  
    Port Scan \MyComment{& single} & TCP \MyComment{& Discovers open ports in a host} & \scriptsize{flags: A; ack: 0;dsize: 0;} \\
    SYN Flood \MyComment{& multiple} & TCP \MyComment{& Denial of Service} & \scriptsize{flags: S,12; threshold: type both, track by\_dst, count 5000, seconds 5;}\\
    UDP Flood \MyComment{& multiple} & UDP \MyComment{& Denial of Service} & \scriptsize{fragbits:M; threshold: type both, track by\_dst, count 5000, seconds 5;} \\
    \bottomrule
  \end{tabular}
\end{table*}

This section reports on the evaluation of \tname{}.

@@

\subsubsection{Malicious traffic.}To reproduce the malicious traffic, we
configured an HTTP server (Apache2) in one machine and ran
Nikto2~\cite{nikto} in a different machine. We used this setup to
replay each of the attacks from Table~\ref{table:attacks}.  On each
execution, we captured the incoming traffic to the web server with
Wireshark~\cite{wireshark-net-monitor} and used the corresponding pcap
files as an input to \tname.\Mar{@Lucas, eu traduzi o que vc. falou
  para ingles. Mas, aparentemente, isto esta **inconsistente** com o
  que eh dito na Secao~\ref{attack-reproduction}. Por favor, esclareca!}

\subsubsection{Benign traffic.}\tname{} uses public databases storing benign
traffic for all protocols covered by Suricata (see
Figure~\ref{fig:distribution-rules-protocol}). We used two datasets of
benign traffic. The Bigflows.pcap dataset is part of the
TcpReplay~\cite{tcpreplay} open source project. This dataset includes
real network traffic of a busy private network access point to the
Internet. According to the TcpReplay web site ``This capture is much
larger and has a smaller average packet size than the previous capture
(smallFlows.pcap). It also has many more flows and different
applications.''. In addition to the Bigflows.pcap dataset, we also
used datasets of normal traffic made available by Stratosphere
Lab~\cite{stratosphere-normal}.

\subsubsection{Ground Truth.}To evaluate precision of \tname\ we
need rules that are considered correct to use as reference. The rules
that detect the attacks from Table~\ref{table:attacks} were obtained
from the Emerging Threats Open Ruleset~\cite{emerging-threats-open}.

@@

@@

\subsubsection{Attack reproduction.}\label{attack-reproduction} \tname{} requires the attack to
be replayed in order to check whether or not the rule it generates
captures the attack.  See function $\mathit{isPlausible}$, used in the
minimization algorithm from Section~\ref{sec:minimization}. For all
attacks listed on Table~\ref{table:attacks}, we found scripts
available on the web to replay the attacks. For example, the SYN Flood
attack can be replayed with hping3~\cite{hping3}, using the following
command: \CodeIn{hping3 -d 80 -w 64 -S -p 80 --flood --rand-source
  <IP>}. With the script to reproduce the attack, we executed the
following steps to obtain ``pcap'' files, which abstracts network
messages~\cite{pcap}, to run \tname:~1)~instantiate the script (\eg{},
define the IP, for the example above), 2)~execute the script,
3)~monitor the traffic with the wireshark network
monitor~\cite{wireshark-net-monitor}.

@@

\subsection{Results}
